Notes for Week 1/23/20 - 1/30/20

### 2020-08-19 notes/weekly_notes/1.30.20.NotesForWeek.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}

@@

% \newcommand{\span}{\textrm{span}}

@@

Let $t$ be an integer, $n = t^d$, and 
\begin{equation*}
\overline{X} := \Bigl\{\frac{1}{t}(j_1,\ldots,j_d): k \in [t]^d\Bigr\}
\end{equation*}
consist of $n$ total evenly spaced grid points on $[0,1]^d$. The lattice graph formed over these grid points is 
\begin{equation*}
\overline{G} := \bigl(\overline{X},\overline{E}\bigr),~~ \overline{E} := \set{(\overline{x},\overline{x}'): \norm{\overline{x} - \overline{x}'}_1 = \frac{1}{t}}.
\end{equation*}
We observe $n$ samples according to regression model
\begin{equation}
\label{eqn:grid_regression_model}
y_j = f(\ol{x}_j) + \varepsilon_j, ~\varepsilon_j \overset{\mathrm{i.i.d}}{\sim} \mathcal{N}(0,1) ~~\textrm{for each $j \in [t]^d$,}
\end{equation}
and our goal is to perform the goodness-of-fit test
\begin{equation*}
\mathbb{H}_0 : f = f_0 := 0 ~~\textrm{vs.}~~ \mathbb{H}_a: f \neq f_0.
\end{equation*}
For a given test $\phi:\Reals^n \to \{0,1\}$ and function class $\mathcal{F}$, we evaluate $\phi$ through the lens of worst-case risk:
\begin{equation*}
\mathcal{R}(\phi; \mathcal{F}) := \Ebb_{f_0}(\phi) + \sup_{f \neq f_0 \in \mathcal{F}}\Ebb_{f}(1 - \phi)
\end{equation*}
Unless there exists some separation between functions $f \in \mathcal{F}$ and $f_0$, the type II error can be quite close to $1$. We enforce this separation by removing a ball of radius $\epsilon$ centered at $f_0$ from the function class $\mathcal{F}$, and let
\begin{equation*}
\mathcal{F}_{\epsilon} := \set{f \in \mathcal{F}: \norm{f}_{\Leb^2} \geq \epsilon}.
\end{equation*}
A classical way to study the properties of $\phi$ over $\mathcal{F}$ is through the critical radius: the smallest value of $\epsilon$ such that $\phi$ has small worst-case risk over the remaining function class $\mathcal{R}(\phi;\mathcal{F}_{\epsilon})$, which we shall write as $\mathcal{R}_{\epsilon}(\phi;\mathcal{F})$.

\section{Graph Laplacian Eigenvector Projection Test}
For an arbitrary graph $G$ on $n$ nodes with graph Laplacian $L_G = D_G - A_G$, let $\Lambda(G)$ consist of the eigenvalues $0 = \lambda_1(G) \leq \lambda_2(G) \leq \cdots \leq \lambda_n(G)$ of $L_G$, with $v_k(G) = (v_{k,1}(G),\ldots,v_{k,n}(G)) \in \Reals^n$ denoting the eigenvector corresponding to the $i$th eigenvalues $\lambda_k(G)$. The graph Laplacian eigenvector projection test is a truncated-series test; letting $\kappa$ be some integer between $1$ and $n$ which indicates where we truncate the series $\bigl(Y^T v_k(G)\bigr)$, our test statistic is
\begin{equation*}
T_{\mathrm{spec}}(G) := \frac{1}{n} \sum_{k = 1}^{\kappa} \Biggl(\sum_{i = 1}^{n} y_i v_{k,i}(G)\Biggr)^2
\end{equation*}
and the test $\phi_{\spec}(G) := \1\{T_{\spec}(G) \geq \tau\}$ rejects the null hypothesis when the test statistic $T_{\mathrm{spec}}(G)$ is greater than a pre-specified cutoff $\tau$.

The truncation level $\kappa$ and cutoff $\tau$ are user-specified hyperparameters. When they are appropriately chosen, the test $\phi_{\spec}(\overline{G})$ is minimax optimal over the Holder ball $C^{1}(\Xset;R)$ when $d \leq 4$.
\begin{theorem}
	\label{thm:holder_testing_rate_grid}
	Let $b \geq 1$ and $R > 0$ be fixed constants, and let $d \leq 4$. Suppose we observe data according to the model~\eqref{eqn:grid_regression_model}. Then when the test $\phi_{\spec}(\overline{G})$ is performed with the parameter choices
	\begin{equation*}
	\kappa = n^{2d/(4 + d)},~~ \tau = \frac{\kappa}{n} + b\sqrt{\frac{2\kappa}{n^2}}
	\end{equation*}
	the following statement is true: there exists a constant $c$ such that for 
	\begin{equation}
	\label{eqn:holder_testing_rate_grid_1}
	\epsilon^2 \geq c R^2 b^2 n^{-4/(4 + d)}
	\end{equation}
	the worst-case risk of $\phi_{\spec}(\overline{G})$ on $C^{1}(\Xset;R)$ is upper bounded
	\begin{equation}
	\label{eqn:holder_testing_rate_grid_2}
	\mathcal{R}_{\epsilon}\Bigl(\phi_{\spec}(\overline{G});C^{1}(\Xset;R)\Bigr) \leq \frac{1}{b}
	\end{equation}
\end{theorem}
The minimax rate for this problem is established by \textcolor{red}{(Abramovich, De Feis, Sapatinas)}, who consider the more general question of testing over Besov spaces. The test they use to establish the upper bound is related to our own, however, they use a continuum wavelet basis orthogonalized in $L^2([0,1]^d)$ rather than the grid Laplacian eigenvectors we consider.

@@

\begin{lemma}
	\label{lem:fixed_graph_testing}
	Let $b \geq 1$ be a fixed constant. Suppose we observe data $Y$ according to the model~\eqref{eqn:regression_model_fixed_graph}, and perform the test $\phi_{\spec}(G)$ for some $1 \leq \kappa \leq n$ and
	\begin{equation*}
	\tau = \frac{\kappa}{n} + b\sqrt{\frac{2\kappa}{n^2}}.
	\end{equation*}
	Then the following statements are true:
	\begin{enumerate}
		\item \textbf{Type I error:} Under the null hypothesis $\beta = \beta_0 = 0$, the Type I error of $\phi_{\spec}(G)$ is upper bounded
		\begin{equation}
		\label{eqn:graph_spectral_type_I_error}
		\mathbb{E}_{\beta_0}\bigl(\phi_{\spec}(G)\bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error:} For any $\beta \in \Reals^n$ such that
		\begin{equation}
		\label{eqn:fixed_graph_testing_critical_radius}
		\frac{1}{n} \sum_{i = 1}^{n} \beta_i^2 \geq 2b\sqrt{\frac{2\kappa}{n^2}} + \frac{\beta^T \bigl(L_G\bigr)^s \beta}{n\bigl[\lambda_{\kappa}(G)\bigr]^s}
		\end{equation}
		the Type II error of $\phi_{\spec}$ is upper bounded,
		\begin{equation}
		\label{eqn:graph_spectral_type_II_error}
		\mathbb{E}_{\beta}\bigl(1 - \phi_{\spec}(G)\bigr) \leq \frac{3}{b}.
		\end{equation}
	\end{enumerate}
\end{lemma}
The proof of Lemma~\ref{lem:fixed_graph_testing} can be seen in the \textit{graph\_testing} document. The eigenvalues of the lattice $\ol{G}$ are known exactly, and standard manipulations \textcolor{red}{Sadhanala} lead to the lower bound
\begin{equation}
\label{eqn:eigenvalue_tail_bound_grid}
\lambda_k(\ol{G}) \geq c n^{-2/d}k^{2/d}~\textrm{for $k = 1,\ldots,n$.}
\end{equation}

@@

	For every $f \in C^1(\Xset;R)$,
	\begin{equation}
	\label{eqn:discrete_sobolev_norm_grid}
	f^T \bigl(L_{\ol{G}}\bigr) f \leq 4R^2 n^{1 - 2/d}
	\end{equation}
	\item 
	\label{event:test_2}

	When $d \leq 4$, for every $f \in C^1(\Xset;R)$ satisfying $\norm{f}_{\Leb^2(\Xset)} \geq R^2 n^{-2/(4 + d)}$, additionally
	\begin{equation}
	\label{eqn:l2_to_empirical_norm_grid}
	\frac{1}{n}\sum_{i = 1}^{n} f(x_i)^2 \geq \frac{1}{4}\norm{f}_{\Leb^2(\Xset)}^2
	\end{equation}
\end{enumerate}
Once we have shown these inequalities, some basic algebra yields that for the specific choice $\kappa = (Rn)^{2d/(4s + d)}$ and a sufficiently large choice of $c$ in \eqref{eqn:holder_testing_rate_grid_1},
\begin{align*}
2b\sqrt{\frac{2\kappa}{n^2}} + \frac{f^T \bigl(L_{\ol{G}}\bigr)^s f}{n\bigl[\lambda_{\kappa}(\ol{G})\bigr]^s} \leq \frac{1}{n}\sum_{i = 1}^{n}\bigl[f(x_i)\bigr]^2
\end{align*}
and~\eqref{eqn:holder_testing_rate_grid_2} follows from Lemma~\ref{lem:fixed_graph_testing}.

\paragraph{Proof of~\eqref{eqn:discrete_sobolev_norm_grid}:}
The upper bound~\eqref{eqn:discrete_sobolev_norm_grid} follows straightforwardly from the Holder property,
\begin{align*}
f^T (L_{\ol{G}}) f & = \sum_{i \in [t]^d} \sum_{j \in [t]^d} \bigl(f(\ol{x}_i) - f(\ol{x}_j\bigr)^2 \1\{\norm{i - j}_1 = t\} \\
& \leq R^2 \sum_{i \in [t]^d} \sum_{j \in [t]^d} \norm{\ol{x}_i - \ol{x}_j}_2^2 \cdot  \1\{\norm{i - j}_1 = t\} \\
& = R^2 n^{-2/d} \sum_{i \in [t]^d} \sum_{j \in [t]^d} \1\{\norm{i - j}_1 = t\}  \\
& \leq 4 R^2 n^{1 - 2/d}.
\end{align*}

\paragraph{Proof of~\eqref{eqn:l2_to_empirical_norm_grid}:}
For $x \in \Rd$, let $Q(x)$ be the $d$-dimensional cube of side length $1/t$ with $x$ at its corner,
\begin{equation*}
Q(x) = [x_1 - 1/t,x_1] \otimes \cdots \otimes [x_d - 1/t,x_d]
\end{equation*}
The difference between $f(\ol{x})$ and the average of $f$ over the cube $Q(\ol{x})$ can be bounded using the Holder property,
\begin{equation*}
\int_{Q(\ol{x})} (f(x) - f(\ol{x}))^2 \,dx \leq \frac{1}{n} R^2 n^{-2/d}.
\end{equation*}
Dividing $\Xset$ into cubes and summing over the cubes, we have
\begin{align*}
\norm{f}_{\Leb^2(\Xset)}^2 & = \sum_{j \in [t]^d} \int_{Q(\ol{x}_j)} \bigl[f(x)\bigr]^2 \,dx \\
& \leq 2 \sum_{j \in [t]^d} \frac{1}{n} \Bigl\{\bigl[f(\ol{x}_j)\bigr]^2 + \int_{Q(\ol{x}_j)} \bigl[f(x) - f(\ol{x}_j)]^2 \,dx \Bigr\} \\
& \leq \frac{2}{n}\sum_{j \in [t]^d} \bigl[f(\ol{x}_j)\bigr]^2 + R^2n^{-2/d} \\
& \leq \frac{2}{n}\sum_{j \in [t]^d} \bigl[f(\ol{x}_j)\bigr]^2 + \frac{1}{2}\norm{f}_{\Leb^2(\Xset)}^2
\end{align*}
where the last inequality follows by the assumption $\norm{f}_{\Leb^2(\Xset)}^2 \geq R^2n^{-4/(4 + d)}$ along with the fact that $4/(4 + d) \leq 2/d$ when $d \leq 4$.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}

@@

@@

Let $N$ be an integer, $n = N^d$, and 
\begin{equation*}
\wb{X} := \Bigl\{\frac{1}{N}(j_1 - 1/2,\ldots,j_d - 1/2): j \in [N]^d\Bigr\}
\end{equation*}
consist of $n$ total evenly spaced grid points on $[0,1]^d$. The lattice graph formed over these grid points is 
\begin{equation*}
\wb{G} := \bigl(\wb{X},\wb{E}\bigr),~~ \wb{E} := \set{(\wb{x},\wb{x}'): \norm{\wb{x} - \wb{x}'}_1 = \frac{1}{t}}.
\end{equation*}
We observe $n$ samples according to regression model
\begin{equation}
\label{eqn:grid_regression_model}
y_j = f(\wb{x}_j) + \varepsilon_j, ~\varepsilon_j \overset{\mathrm{i.i.d}}{\sim} \mathcal{N}(0,1) ~~\textrm{for each $j \in [t]^d$,}
\end{equation}
and our goal is to perform the goodness-of-fit test
\begin{equation*}
\mathbb{H}_0 : f = f_0 := 0 ~~\textrm{vs.}~~ \mathbb{H}_a: f \neq f_0.
\end{equation*}
For a given test $\phi:\Reals^n \to \{0,1\}$ and function class $\mathcal{F}$, we evaluate $\phi$ through the lens of worst-case risk:
\begin{equation*}
\mathcal{R}(\phi; \mathcal{F}) := \Ebb_{f_0}(\phi) + \sup_{f \neq f_0 \in \mathcal{F}}\Ebb_{f}(1 - \phi)
\end{equation*}
Unless there exists some separation between functions $f \in \mathcal{F}$ and $f_0$, the type II error can be quite close to $1$. We enforce this separation by removing a ball of radius $\epsilon$ centered at $f_0$ from the function class $\mathcal{F}$, and let
\begin{equation*}
\mathcal{F}_{\epsilon} := \set{f \in \mathcal{F}: \norm{f}_{\Leb^2} \geq \epsilon}.
\end{equation*}
A classical way to study the properties of $\phi$ over $\mathcal{F}$ is through the critical radius: the smallest value of $\epsilon$ such that $\phi$ has small worst-case risk over the remaining function class $\mathcal{R}(\phi;\mathcal{F}_{\epsilon})$, which we shall write as $\mathcal{R}_{\epsilon}(\phi;\mathcal{F})$.

\section{Graph Laplacian Eigenvector Projection Test}
For an arbitrary graph $G$ on $n$ nodes with graph Laplacian $L_G = D_G - A_G$, let $\Lambda(G)$ consist of the eigenvalues $0 = \lambda_1(G) \leq \lambda_2(G) \leq \cdots \leq \lambda_n(G)$ of $L_G$, with $v_k(G) = (v_{k,1}(G),\ldots,v_{k,n}(G)) \in \Reals^n$ denoting the eigenvector corresponding to the $i$th eigenvalues $\lambda_k(G)$. The graph Laplacian eigenvector projection test is a linear projection test; letting $\kappa$ be some integer between $1$ and $n$, we define $\Pi_{k,G}(\theta) := \frac{1}{\sqrt{n}}\sum_{k = 1}^{\kappa} \dotp{v_k}{\theta}$ to be a suitable rescaling of the projection of $\theta$ onto the span of $v_1(G),\ldots,v_k(G)$.

Our test statistic
\begin{equation*}
T_{\mathrm{spec}}(G) := \norm{\Pi_{\kappa,G}(Y)}_n^2 - \frac{\kappa}{n}
\end{equation*}
is a simple function of the projection of the data $Y$ onto the span of the first $\kappa$ eigenvectors of the graph Laplacian $L(G)$ -- it is a standard calculation to show that
\begin{equation*}
\Ebb_{Y|X}\Bigl[\norm{\Pi_{\kappa,G}(Y)}_n^2\Bigr] = \norm{\Pi_{\kappa,G}(f)}_n^2 + \frac{\kappa}{n}
\end{equation*}
and hence our test statistic is an unbiased estimate of the norm $\norm{\Pi_{\kappa,G}(f)}_n^2$. The graph Laplacian eigenvector test $\phi_{\spec}(G) := \1\{T_{\spec}(G) \geq \tau(b)\}$ rejects the null hypothesis when the test statistic $T_{\mathrm{spec}}(G)$ is greater than a pre-specified cutoff $\tau(b)$, where the number $b$---or more precisely, $1/b$---encodes the level of error the user is willing to tolerate.

The number of eigenvectors $\kappa$ and cutoff $\tau(b)$ are user-specified hyperparameters. When they are appropriately chosen, the test $\phi_{\spec}(\wb{G})$ is minimax optimal over the Holder ball $C^{1}(\Xset;R)$ when $d \leq 4$.
\begin{theorem}
	\label{thm:holder_testing_rate_grid}
	Let $L > 0$ be a fixed constant, and let $d \leq 4$. Suppose we observe data according to the model~\eqref{eqn:grid_regression_model}. Then when the test $\phi_{\spec}(\wb{G})$ is performed with the parameter choices
	\begin{equation*}
	\kappa = n^{2d/(4 + d)},~~ \tau(b) = b\sqrt{\frac{2\kappa}{n^2}}
	\end{equation*}
	for some $b \geq 1$, the following statement is true: there exists a constant $c$ such that for 
	\begin{equation}
	\label{eqn:holder_testing_rate_grid_1}
	\epsilon^2 \geq c L^2 b^2 n^{-4/(4 + d)}
	\end{equation}
	the worst-case risk of $\phi_{\spec}(\wb{G})$ on $C^{1}(\Xset;L)$ is upper bounded
	\begin{equation}
	\label{eqn:holder_testing_rate_grid_2}
	\mathcal{R}_{\epsilon}\Bigl(\phi_{\spec}(\wb{G});C^{1}(\Xset;L)\Bigr) \leq \frac{1}{b}.
	\end{equation}
\end{theorem}
The minimax rate for this problem is established by \textcolor{red}{(Abramovich, De Feis, Sapatinas)}, who consider the more general question of testing over Besov spaces. The test they use to establish the upper bound is related to our own, however, they use a continuum wavelet basis orthogonalized in $L^2([0,1]^d)$ rather than the grid Laplacian eigenvectors we consider.

As was the case with the neighborhood graph in the random design setting, the grid Sobolev norm fails to track the higher order derivatives of $f$ near the boundary of $\Xset$. We therefore must insist that $f$ be compactly supported in order for the grid eigenvector projection test to achieve minimax optimal testing rates over higher-order Holder classes.

\begin{theorem}
	\label{thm:holder_testing_rate_grid_higher_order}
	Let $L > 0$ be fixed constants, $s \geq 2$ be a fixed integer, and let $d \leq 4s$.  Suppose we observe data according to the model~\eqref{eqn:grid_regression_model}. Then when the test $\phi_{\spec}(\wb{G})$ is performed with the parameter choices
	\begin{equation*}
	\kappa = n^{2d/(4s + d)},~~ \tau(b) =  b\sqrt{\frac{2\kappa}{n^2}}
	\end{equation*} 
	for some $b \geq 1$, the following statement is true: there exists a constant $c$ such that for any
	\begin{equation*}
	\epsilon^2 \geq c L^2 b^2 n^{-4s/(4s + d)},
	\end{equation*}
	the worst-case risk of $\phi_{\spec}(\wb{G})$ is upper bounded
	\begin{equation*}
	\mathcal{R}_{\epsilon}\Bigl(\phi_{\spec}(\wb{G});C_c^{s}(\Xset;L)\Bigr) \leq \frac{1}{b}.
	\end{equation*}
\end{theorem}

In order to prove Theorems~\ref{thm:holder_testing_rate_grid} and~\ref{thm:holder_testing_rate_grid_higher_order}, we decompose
\begin{equation*}
T_{\spec}(\wb{G}) - \norm{f}_{\Leb^2}^2 = \Bigl\{\norm{\Pi_{\kappa,\wb{G}}Y}_n^2 - \frac{\kappa}{n} - \norm{\Pi_{\kappa,\wb{G}}f}_n^2\Bigr\} + \Bigl\{\norm{\Pi_{\kappa,\wb{G}}f}_n^2 - \norm{f}_n^2\Bigr\} + \Bigl\{\norm{f}_n^2 - \norm{f}_{\Leb^2}^2\Bigr\},
\end{equation*}
where we refer to the three terms on the right hand side as the estimation error, approximation error, and the discretization error, respectively.

Our technical work consists of upper bounding these three sources of error. When $4s \geq d$, the discretization error is negligible regardless of our choice of $\kappa$, and we focus our attention on minimizing the sum of approximation and estimation errors. This is the standard tradeoff in nonparametric testing problems, and the usual choice of projecting our data $Y \in \Reals^n$ onto a subspace of dimension $\kappa = n^{2d/(4s + d)}$ balances the contribution of these two terms.

\subsection{Low-smoothness regime}
In the low-smoothness regime $d > 4s$, the coupling between empirical norm over $\wb{X}$ and the continuum $\Leb^2$ norm is sufficiently weak that the discretization error can become the dominant source of error, as we show in Lemma~\ref{lem:holder_testing_rate_grid_low_smoothness_lb}.

\begin{lemma}
	\label{lem:holder_testing_rate_grid_low_smoothness_lb}
	For any $L > 0$ and any integers $s$ and $d$, there exists a function $f \in C^s(\Xset;L)$ such that
	\begin{equation*}
	\norm{f}_{\Leb^2}^2 \geq \frac{1}{2^d} L^2 n^{-2s/d} 
	\end{equation*}
	but $f(\wb{x}) = 0$ for all $\wb{x} \in \wb{X}$. 
\end{lemma}
Lemma~\ref{lem:holder_testing_rate_grid_low_smoothness_lb} implies the critical radius over the Holder classes $C^s(\Xset;L)$ must be at least on the order of $\epsilon^{\star}(C^s(\Xset;L)) \gtrsim n^{-s/d}$. When $4s \geq d$, this term is neglible relative to $n^{-2s/(4s + d)}$, and we arrive at the ``usual'' rates of minimax testing we see in Theorems~\ref{thm:holder_testing_rate_grid} and~\ref{thm:holder_testing_rate_grid_higher_order}. On the other hand when $4s < d$, this becomes the dominant term, and we can no longer achieve the typical rate $\epsilon^2 \asymp n^{-4s/(4s + d)}$.

In this setting, when we enforce the wider radius $\epsilon^2 \asymp n^{-2s/d}$, Proposition~\ref{prop:holder_testing_rate_grid_low_smoothness_ub} shows that a very simply test has small worst-case risk $\mathcal{R}_{\epsilon}$.

\begin{proposition}
	\label{prop:holder_testing_rate_grid_low_smoothness_ub}
	Let $L > 0$ be a fixed constant, $s \geq 1$ a fixed integer, and let $d \geq 4s$. Suppose we observe data according to the grid design regression model~\eqref{eqn:grid_regression_model}. Then when the test $\phi_{\spec}(\wb{G})$ is performed with the parameter choices
	\begin{equation*}
	\kappa = n,~~ \tau(b) = b\sqrt{\frac{2}{n}}
	\end{equation*}
	for some $b \geq 1$, the following statement is true: there exists a constant $c$ such that for any 
	\begin{equation*}
	\epsilon^2 \geq c b^2 L^2 n^{-2s/d}
	\end{equation*}
	the worst case risk of $\phi_{\spec}(\wb{G})$ is upper bounded
	\begin{equation*}
	\mathcal{R}_{\epsilon}(\phi_{\spec}(\wb{G}); C^s(\Xset;L)) \leq \frac{1}{b}. 
	\end{equation*}
\end{proposition}

\begin{itemize}
	\item The test statistic $T_{\spec}(\wb{G})$ is simply the empirical norm of $Y$. 
	\item Together, Lemma~\ref{lem:holder_testing_rate_grid_low_smoothness_lb} and Proposition~\eqref{prop:holder_testing_rate_grid_low_smoothness_ub} characterize the minimax rate of the grid design regression testing problem when $4s > d$.
	\item This minimax rate does not match the upper bound established in Proposition~\textcolor{red}{(Holder testing random design)}---the fixed design problem is harder. 
	\item Note that the usual minimax rate of estimation error over Holder classes is always $n^{-2s/(2s + d)}$, regardless of the relation between $s$ and $d$, and regardless of whether loss is measured in $\Leb^2$-norm or empirical norm. The explanation for this is that the rate $n^{-2s/(2s + d)}$ is always larger than $n^{-2s/d}$, and so the discretization error is never the dominant source of error in estimation. This reveals an interesting distinction between the testing and estimation problems, as testing is easy enough in a statistical sense that error incurred by the discrete nature of the problem may be the bottleneck.
\end{itemize}

\subsection{Continuum Sobolev class.}

Now suppose we assume $f \in H^s(\Xset;L)$ belongs to a relevant Sobolev ball, rather than a Holder ball, and we again ask about the worst case risk $\mathcal{R}_{\epsilon}(\phi;H^s(\Xset;L))$.

When $2s < d$, the situation is hopeless. The Sobolev class $H^s(\Xset;L)$ includes bump functions of arbitrarily small radius and arbitrarily large height---in the limit, delta functions. By placing these bump functions at design points $\wb{x}$, we can construct a function $f$ which satisfies $f \equiv L$ almost everywhere on $\Xset$, while $f(\wb{x}) = 0$ for all $\wb{x} \in \wb{X}$. No test based on data observed according to model~\eqref{eqn:grid_regression_model} can have more than trivial power against $f$, implying that for all tests $\phi$ the worst case risk $\mathcal{R}_{\epsilon}(\phi;H^s(\Xset;L))$ is $1$ unless $\epsilon = \Omega(1)$.

When $2s > d$, we are not sure how the situation changes. The Sobolev Embedding Theorem gives us that the critical radius 
\begin{equation*}
\epsilon^{\star}\bigl(H^s(\Xset;L)\bigr) \leq c \epsilon^{\star}\bigl(C^{s'}(\Xset;L)\bigr),~~\textrm{for $s' = s - d/2$.}
\end{equation*}
where we recall that the critical radius over Holder functions is
\begin{equation*}
\epsilon^{\star}\bigl(C^{s}(\Xset;L)\bigr) \asymp \max\bigl\{n^{-2s/(4s + d)}, n^{-s/d}\bigr\}
\end{equation*}
We might hope to do better, but it is hard to say.

@@

\begin{lemma}
	\label{lem:fixed_graph_testing}
	Let $b \geq 1$ be a fixed constant. Suppose we observe data $Y$ according to the model~\eqref{eqn:regression_model_fixed_graph}, and perform the test $\phi_{\spec}(G)$ for some $1 \leq \kappa \leq n$ and
	\begin{equation*}
	\tau = b\sqrt{\frac{2\kappa}{n^2}}.
	\end{equation*}
	Then the following statements are true:
	\begin{enumerate}
		\item \textbf{Type I error:} Under the null hypothesis $\beta = \beta_0 = 0$, the Type I error of $\phi_{\spec}(G)$ is upper bounded
		\begin{equation}
		\label{eqn:graph_spectral_type_I_error}
		\mathbb{E}_{\beta_0}\bigl(\phi_{\spec}(G)\bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error:} For any $\beta \in \Reals^n$ such that
		\begin{equation}
		\label{eqn:fixed_graph_testing_critical_radius}
		\frac{1}{n} \sum_{i = 1}^{n} \beta_i^2 \geq 2b\sqrt{\frac{2\kappa}{n^2}} + \frac{\beta^T \bigl(L_G\bigr)^s \beta}{n\bigl[\lambda_{\kappa}(G)\bigr]^s}
		\end{equation}
		the Type II error of $\phi_{\spec}$ is upper bounded,
		\begin{equation}
		\label{eqn:graph_spectral_type_II_error}
		\mathbb{E}_{\beta}\bigl(1 - \phi_{\spec}(G)\bigr) \leq \frac{3}{b}.
		\end{equation}
	\end{enumerate}
\end{lemma}
The proof of Lemma~\ref{lem:fixed_graph_testing} can be seen in the \textit{graph\_testing} document. The eigenvalues of the lattice $\wb{G}$ are known exactly, and standard manipulations \textcolor{red}{Sadhanala} lead to the lower bound
\begin{equation}
\label{eqn:eigenvalue_tail_bound_grid}
\lambda_k(\wb{G}) \geq c n^{-2/d}k^{2/d}~\textrm{for $k = 1,\ldots,n$.}
\end{equation}

@@

	For every $f \in C^1(\Xset;R)$,
	\begin{equation}
	\label{eqn:discrete_sobolev_norm_grid}
	f^T \bigl(L_{\wb{G}}\bigr) f \leq 4R^2 n^{1 - 2/d}
	\end{equation}
	\item 
	\label{event:test_2}

	When $d \leq 4$, for every $f \in C^1(\Xset;R)$ satisfying $\norm{f}_{\Leb^2(\Xset)} \geq R^2 n^{-2/(4 + d)}$, additionally
	\begin{equation}
	\label{eqn:l2_to_empirical_norm_grid}
	\frac{1}{n}\sum_{i = 1}^{n} f(x_i)^2 \geq \frac{1}{4}\norm{f}_{\Leb^2(\Xset)}^2
	\end{equation}
\end{enumerate}
Once we have shown these inequalities, some basic algebra yields that for the specific choice $\kappa = (Rn)^{2d/(4s + d)}$ and a sufficiently large choice of $c$ in \eqref{eqn:holder_testing_rate_grid_1},
\begin{align*}
2b\sqrt{\frac{2\kappa}{n^2}} + \frac{f^T \bigl(L_{\wb{G}}\bigr)^s f}{n\bigl[\lambda_{\kappa}(\wb{G})\bigr]^s} \leq \frac{1}{n}\sum_{i = 1}^{n}\bigl[f(x_i)\bigr]^2
\end{align*}
and~\eqref{eqn:holder_testing_rate_grid_2} follows from Lemma~\ref{lem:fixed_graph_testing}.

\paragraph{Proof of~\eqref{eqn:discrete_sobolev_norm_grid}:}
The upper bound~\eqref{eqn:discrete_sobolev_norm_grid} follows straightforwardly from the Holder property,
\begin{align*}
f^T (L_{\wb{G}}) f & = \sum_{i \in [t]^d} \sum_{j \in [t]^d} \bigl(f(\wb{x}_i) - f(\wb{x}_j\bigr)^2 \1\{\norm{i - j}_1 = t\} \\
& \leq R^2 \sum_{i \in [t]^d} \sum_{j \in [t]^d} \norm{\wb{x}_i - \wb{x}_j}_2^2 \cdot  \1\{\norm{i - j}_1 = t\} \\
& = R^2 n^{-2/d} \sum_{i \in [t]^d} \sum_{j \in [t]^d} \1\{\norm{i - j}_1 = t\}  \\
& \leq 4 R^2 n^{1 - 2/d}.
\end{align*}

\paragraph{Proof of~\eqref{eqn:l2_to_empirical_norm_grid}:}
For $x \in \Rd$, let $Q(x)$ be the $d$-dimensional cube of side length $1/t$ with $x$ at its corner,
\begin{equation*}
Q(x) = [x_1 - 1/t,x_1] \otimes \cdots \otimes [x_d - 1/t,x_d]
\end{equation*}
The difference between $f(\wb{x})$ and the average of $f$ over the cube $Q(\wb{x})$ can be bounded using the Holder property,
\begin{equation*}
\int_{Q(\wb{x})} (f(x) - f(\wb{x}))^2 \,dx \leq \frac{1}{n} R^2 n^{-2/d}.
\end{equation*}
Dividing $\Xset$ into cubes and summing over the cubes, we have
\begin{align*}
\norm{f}_{\Leb^2(\Xset)}^2 & = \sum_{j \in [t]^d} \int_{Q(\wb{x}_j)} \bigl[f(x)\bigr]^2 \,dx \\
& \leq 2 \sum_{j \in [t]^d} \frac{1}{n} \Bigl\{\bigl[f(\wb{x}_j)\bigr]^2 + \int_{Q(\wb{x}_j)} \bigl[f(x) - f(\wb{x}_j)]^2 \,dx \Bigr\} \\
& \leq \frac{2}{n}\sum_{j \in [t]^d} \bigl[f(\wb{x}_j)\bigr]^2 + R^2n^{-2/d} \\
& \leq \frac{2}{n}\sum_{j \in [t]^d} \bigl[f(\wb{x}_j)\bigr]^2 + \frac{1}{2}\norm{f}_{\Leb^2(\Xset)}^2
\end{align*}
where the last inequality follows by the assumption $\norm{f}_{\Leb^2(\Xset)}^2 \geq R^2n^{-4/(4 + d)}$ along with the fact that $4/(4 + d) \leq 2/d$ when $d \leq 4$.

\subsection{Proof of Theorem~\ref{thm:holder_testing_rate_grid_higher_order}}
Referring again to Lemma~\ref{lem:fixed_graph_testing}, to prove Theorem~\ref{thm:holder_testing_rate_grid_higher_order} it will be sufficient to prove the following inequalities
\begin{enumerate}[label=(E\arabic*)]
	\item 
	\label{event:grid_sobolev_norm_higher_order}
	For any $f \in C_c^s(\Xset;L)$,
	\begin{equation}
	\label{eqn:grid_sobolev_norm_higher_order}
	f^T \wb{L}^s f \leq c L^2 n^{1 - 2s/d}.
	\end{equation}
	\item 
	\label{event:grid_empirical_norm_higher_order}
	There exists a sufficiently small constant $c_1$ and a sufficiently large constant $c_2$ such that for any $f \in C^s(\Xset;L)$,
	\begin{equation}
	\label{eqn:grid_empirical_norm_higher_order}
	c_1 \norm{f}_n^2 \geq \norm{f}_{\Leb^2(\Xset)}^2 - c_2 L n^{-2s/d}
	\end{equation}
	for all $n$ sufficiently large.
\end{enumerate}
The proof of \eqref{eqn:grid_empirical_norm_higher_order} is the content of Lemma~\ref{lem:discretization_error_holder}. Here, we focus our attention on proving~\eqref{eqn:grid_sobolev_norm_higher_order}.

To obtain this upper bound, first observe that by letting $D_{e_i^2}f := f(\wb{x} + he_i) + f(\wb{x} - he_i) - 2f(\wb{x})$ and taking a $2$nd order Taylor expansion, for all points $\wb{x} \in \Xset_{h} \cap \wb{X} =: \wb{X}_{h}$ we can express the grid Laplacian as
\begin{align}
\wb{L}f(\wb{x}) & = \sum_{i = 1}^{d} D_{e_i^2}f(\wb{x}) \nonumber \\
& = \sum_{i = 1}^{d} \biggl[\frac{\partial}{\partial e_i} f(\wb{x})(e_ih - e_ih) + \frac{h^2}{2} \int_{-h}^{h} \frac{\partial^2}{\partial e_i^2} f(\wb{x} + e_it) \,dt \biggr] \nonumber \\
& = \frac{h^2}{2} \int_{-h}^{h} \sum_{i = 1}^{d} \frac{\partial^2}{\partial e_i^2} f(\wb{x} + e_it) \,dt \label{eqn:grid_sobolev_norm_higher_order_pf1}
\end{align} 
as a second-order differential operator which roughly approximates the continuum Laplace operator $\Delta = -\sum_{i = 1}^{d} \frac{\partial^2}{\partial e_i^2}$. Motivated by this, in Lemma~\ref{lem:grid_laplacian_approximation_error} we provide estimates on the absolute difference between the action of the iterated grid Laplacian and the iterated continuum Laplace operator. Specifically, we show that at all sufficiently interior points $\wb{x} \in \wb{X} \cap \Xset_{qh}$ 
\begin{equation*}
\begin{rcases*}
